\documentclass{article}

\usepackage[a4paper, left=0.5in,right=0.5in,top=0.5in,bottom=0.5in]{geometry}
\usepackage{paralist}
\usepackage{hyperref}

\pagenumbering{gobble}

\begin{document}
	
	\begin{center}
	\begin{Huge}
	\textbf{Swaminathan Sankararaman}
	\end{Huge}
	\end{center}
	
	\begin{center}Application Support Analyst\end{center}
	
	\vspace{-\baselineskip}\hspace{-1.5em}\hrulefill\vspace{-.7\baselineskip}

	\begin{center}
		\begin{inparaitem}[\hspace{1em}\textbullet]
			\hspace{-1em}\item Chennai,TN,India
			\item swaminathan.sr4@gmail.com
			\item +91-81220-29364
			\item \href{https://www.linkedin.com/in/swaminathan-sankara-raman-79004198/}{LinkedIn}
			\item \href{https://github.com/swami1894}{GitHub}
		\end{inparaitem}
	\end{center}
	
	\section*{Summary \hrulefill\vspace{-.3\baselineskip}}
	\hspace{3em}I am an IT Analyst with Tata Consultancy Services Ltd., with employment experience close to 6 years. I am working as an Application support Analyst for a leading banker in North America. My roles and responsibilities include testing and performance monitoring for a client proprietary file transfer tool during OS patching or uprgade on the application server or during a new version upgrade of the tool. I am also incharge of testing proof of concepts to check for performance improvement of newly introduced solutions, to consider if the implementation of the proposed solution is viable or not. I am looking for opportunites to pursue the role of a Performance Engineer for Software Applications.
	
	\section*{Work Experience \hrulefill\vspace{-.3\baselineskip}}
	\begin{itemize}
		\item \textbf{Tata Consultancy Services India Ltd.}, Chennai, TN, India \hfill August 2023 - Present\\
		\textit{Application Support Analyst}
		\begin{itemize}
			\item Developing test plan and testing client proprietary file transfer tool.
			\item Developing python scripts to perform file delivery and validate the transfer in cleint proprietary file transfer tool across differnt versions of tool to ensure consistency.
			\item Perform tests to validate if there any performance improvment when the new optional features or functionalities are introduced.
			\item Setting up alerts and monitors in application servers using Dynatrace. This was essential during load-testing in lower environments to prevent impact for the other users.
			\item Deployed automated test scripts using Ansible.
			\item Generated reports on user compliance to the policies set by the Application Engineering team to identify gaps and potential opportunities to improve the tool provided.
		\end{itemize}
		\item \textbf{Tata Consultancy Services Canada Ltd.}, Toronto, ON, Canada \hfill March 2022 - July 2023\\
		\textit{Application Support Analyst}
		\begin{itemize}
			\item Created accounts to enable secure file transfer within and outside the organization.
			\item Developed Job Information Language (JIL) to automate the file transfer and file receiving process.
			\item Succeeded in creating Unix scripts to aid file transfer through automated process.
			\item Performed Incident management and Change management services for the Client.
		\end{itemize}
		\item \textbf{Tata Consultancy Services India Ltd.}, Chennai, TN, India \hfill January 2017 - December 2019\\
		\textit{Software Developer, Systems Engineer}
		\begin{itemize}
			\item Developed driver programs capable of creating credit card invoice files for 20 clients, payment processing jobs for 5 clients and bill transmission jobs for over 50 clients of a Global Financial Institution.
        		\item Developed a driver program using COBOL to generate credit card invoice files in a standard file format from unstructured data received from over 20 clients by a leading bank. 
        		\item Developed jobs to process payments for 5 clients using Job Control Language (JCL)
        		\item Scheduled commercial credit card bill transmission jobs for more than 50 clients matching their payment cycle.
        		\item Developed a tracking system for a large client to keep track of their commercial credit card invoices.
        		\item Tracker system combined the results from over 50 different jobs and delivered the client a dash board containing necessary details
        		\item Optimized the production environment by removing over 30 obsolete jobs which costing the client and unnecessary overhead.
        		\item Analyzed over 100s of jobs to identify their dependencies and links in the system to weed out unnecessary jobs from the test and production systems completely to optimize the environment.
		\end{itemize}
	\end{itemize}
	
	\section*{Certifications \hrulefill\vspace{-.3\baselineskip}}
	\begin{itemize}
		\item \textbf{Microsoft Azure Data Fundamentals Certified – DP900} \hfill January 2024\\
		\textbf{Credential ID:} 42D01F87BCCA2F5\\
		\textbf{Certification No:}. 5C75D2-08K458
	\end{itemize}
	
	
	\section*{Education \hrulefill\vspace{-.3\baselineskip}}
	\begin{itemize}
		\item \textbf{University of Guelph}, Guelph, ON, Canada \hfill July 2020 - August 2021\\
			  \textit{Master of Engineering, Engineering} \hfill	Overall CGPA: 3.4/4.0\\
			  Relevant Courses: Machine Learning, Data Analysis, Intelligent Real-Time Systems, Internet of Things
		\item \textbf{Sri Sairam Engineering College}, Chennai, TN, India \hfill August 2012 - April 2016\\
	\textit{Bachelor of Engineering, Engineering} \hfill	Overall CGPA: 7.98/10.0\\
Relevant Courses: Data Structures, Object Oriented Programming, Computer Programming
	\end{itemize}
	
	\section*{Technical Skills \hrulefill\vspace{-.3\baselineskip}}
	\begin{tabular}{l p{13.5cm}}
		\textbf{Programming Languages} & 
		\begin{inparaitem}[\hspace{1em}{\tiny\textbullet}]
			\hspace{-1em}\item Python
			\item SQL
			\item Scala
			\item R
			\item Julia
			\item COBOL
			\item C
			\item C++
			\item JCL
		\end{inparaitem} \\
		\textbf{Developer Tools} & 
		\begin{inparaitem}[\hspace{1em}{\tiny\textbullet}]
			\hspace{-1em}\item Git
			\item Jupyter Notebook
			\item VS Code
			\item PyChar
			\item R Studio
			\item Vim
		\end{inparaitem} \\
		\textbf{Analytics Tool} & 
		\begin{inparaitem}[\hspace{1em}{\tiny\textbullet}]
			\hspace{-1em}\item Microsoft Power BI
			\item MS Excel
			\item Numpy
			\item Pandas
			\item Seaborn
			\item Matplotlib
			\item Scikit-Learn
			\item Spark
			\item Dynatrace
			\item Datadog
		\end{inparaitem} \\	
		\textbf{Operating System} & 
		\begin{inparaitem}[\hspace{1em}{\tiny\textbullet}]
			\hspace{-1em}\item Windows
			\item Red Hat Enterprise Linux (RHEL)
			\item Unix like OS
			\end{inparaitem} \\
	\end{tabular}
	
	\section*{Soft Skills \hrulefill\vspace{-.3\baselineskip}}
	\begin{inparaitem}[\hspace{1em}{\tiny\textbullet}]
			\hspace{-1em}\item Problem Solving
			\item Adaptabiity
			\item Critical Thinking
			\item Learning from others
			\item Communication
			\item Teamwork
		\end{inparaitem} \\	
	
	\hspace{-1.5em}\hrulefill
	
\end{document}